### 2018-05-04 papers/synth/example.tex

We have used our tool to synthesize possible fixes to complete the graph. Variation 1 of our tool adds new labelled edges to the graph. We have ranked the all possible graph edits with simple rank of minimum updates. Our tools was able to complete this graph by adding five new edges and nine new molecules in 210s. Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s. Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s. Variation 4 of our tool synthesis Boolean function based on AND, OR gates. The result shows the basic template of 4 leafs and 3 gates we allow user to provide it's own template in our front end language. The tool was able to synthesize the Boolean functions in 470s.

>>>>

We have used our tool to synthesize possible fixes to complete the graph. Based on the variation we were able to synthesis the this graph within 600s. We have created a rank of minimum edits to complete the graph. Our experiments suggest that the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.

### 2018-05-04 papers/synth/experiments.tex

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
\ashu{@ankit: please discuss all the synthesis queries in the table.}
%
%
Our experiments suggest that the synthesis problems are solvable by modern
solvers and the synthesis technology may be useful for biological research.
%

>>>>

The table shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes
needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
\ashu{@ankit: please discuss all the synthesis queries in the table.}

Variation 1 of our tool adds new labelled edges to the graph. We have ranked the all possible graph edits with the simple rank of minimum updates. Our tools were able to complete this graph by adding five new edges and nine new molecules in 210s. Variation 2 of our graph adds new labels to the edge and was able to fix this graph with eleven new molecule labels in 180s. Variation 3 of our tool synthesis low depth CNF functions and was able to synthesis the result in 500s. Variation 4 of our tool synthesis Boolean function based on AND, OR gates. The result shows the basic template of 4 leaves and 3 gates we allow the user to provide its own template in our front-end language. The tool was able to synthesize the Boolean functions in 470s.
%
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%
